---
title: "World_map"
output: html_document
---

```{r, message = FALSE, warnings = FALSE, echo = FALSE}
#### world visualised, largely plug and play, cheers Josh ####
library(sf) 
library(tmap)
library(tidyverse)
emm75 <- read.csv("/Users/jmmans/Desktop/emm75_meta/emm75in/emm75_meta_analysistime.csv", header = TRUE, row.names = 1)
data(World) #Provides dataset for map geometries```
```

```{r map stuff, fig.height = 7, fig.width = 15}
###### Subset country frequencies in metadata, then make barplot & global map

#Subset country frequencies in Metadata 
Worldfr <- emm75 %>% group_by(Country) %>% count() %>% rename(Frequency = n)

#Change window frame of barplot, make barplot & translate axis names
par(mar=c(14,4,4,4))
barplot(Worldfr$Frequency, names.arg = Worldfr$`Country`, las=2, offset = 0, col="#69b3a2", font.lab=2, 
        xlab = "", ylab = "Frequency in currated dataset", ylim = c(0,250))
mtext(text="Country of S. aureus ST5 isolation",  line=-45)

#Match & align map dataset with metadataset with Country names
Countrynames <- match(World$name, Worldfr$`Country`)
Countrynames <- Worldfr[Countrynames, ]
Worldmap <- st_sf(data.frame(World, Countrynames)) 

#Visualise Worldmap
pics <- tm_shape(Worldmap) + tm_borders() + tm_layout(bg.color = "lightblue") + 
  tm_fill(col = "Frequency", palette = "seq", showNA = FALSE) 

svg(filename="/Users/jmmans/Desktop/emm75_meta/emm75out/source_dist.svg")
pics
dev.off
```
